Type cones of $\b{g}$-vector fans

### 2018-10-05 secondPaper/accordionComplexSurfaces.tex
Schroer
corrections second paper and more on type cones

\maketitle

@@

\enlargethispage{.2cm}
We first quickly review the definition of the non-kissing complex of a gentle bound quiver following the presentation of~\cite{PaluPilaudPlamondon} and extend it to locally gentle bound quivers.

@@

We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a finite quiver~$Q$ and an ideal~$I$ of the path algebra~$kQ$ (the~$k$-vector space generated by all paths in~$Q$, including vertices as paths of length zero, with multiplication induced by concatenation of paths) such that~$I$ is generated by linear combinations of paths of length at least two.
Note that we \textbf{do not require} that the quotient algebra~$kQ/I$ be finite dimensional.
The following definition is adapted from~\cite{ButlerRingel}. We note that it is customary to consider non-finite dimensional gentle algebras in the literature, see e.g.~\cite{Schoer}.

@@

\begin{example}
Considering our choice of conventions, we represent the string ${\rho = \gamma\beta^{-1}\alpha^{-1}\gamma\beta^{-1}\alpha^{-1}\gamma\delta}$ as follows:
\[
\rho = \;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString1}}}
\]
\end{example}

\begin{notation}
To avoid distinguishing between finite, infinite and bi-infinite words, we denote strings as products~$\rho = \prod_{i < \ell < j} \alpha_\ell^{\epsilon_\ell}$ where~$i < j \in \Z \cup \{\pm \infty\}$, $\epsilon_\ell\in\{\pm 1\}$ and~$\alpha_\ell \in Q_1$ for all~$i < \ell < j$.
\end{notation}

@@

A simplicial complex is \defn{thin} if each of its codimension~$1$ face is contained in exaclty two facets.
We state the following results, which generalize \cite[Prop.~2.33 \& Cor.~2.35]{PaluPilaudPlamondon}, whose proofs apply without change.

>>>>

\vspace*{-1cm}
\maketitle
\vspace{-.5cm}

@@

\enlargethispage{.4cm}
We first quickly review the definition of the non-kissing complex of a gentle bound quiver following the presentation of~\cite{PaluPilaudPlamondon} and extend it to locally gentle bound quivers.

@@

We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a finite quiver~$Q$ and an ideal~$I$ of the path algebra~$kQ$ (the~$k$-vector space generated by all paths in~$Q$, including vertices as paths of length zero, with multiplication induced by concatenation of paths) such that~$I$ is generated by linear combinations of paths of length at least two.
Note that we \textbf{do not require} that the quotient algebra~$kQ/I$ be finite dimensional.
The following definition is adapted from~\cite{ButlerRingel}. We note that it is customary to consider non-finite dimensional gentle algebras in the literature, see e.g.~\cite{Schroer}.

@@

\begin{example}
With our choice of conventions, we represent the string ${\gamma\beta^{-1}\alpha^{-1}\gamma\beta^{-1}\alpha^{-1}\gamma\delta}$ by
\[
\;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString1}}}
\]
\end{example}

\begin{notation}
To avoid distinguishing between finite, infinite and bi-infinite words, we denote strings as products~$\rho = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell}$ where~$i < j \in \Z \cup \{\pm \infty\}$, $\varepsilon_\ell\in\{\pm 1\}$ and~$\alpha_\ell \in Q_1$ for all~$i < \ell < j$.
\end{notation}

@@

A simplicial complex is \defn{thin} if each codimension~$1$ face is contained in exactly two facets.
We state the following results, which generalize \cite[Prop.~2.33 \& Cor.~2.35]{PaluPilaudPlamondon}, whose proofs apply without change.

### 2018-10-05 thridPaper/draft/typeConeAssociahedra.tex
corrections second paper and more on type cones

One important observation is that it seems there is ``one extremal exchangeable pair for each positive root'' (or equivalently each positive $c$-vector), meaning that for each positive root~$\beta \in \Phi^+$, there is precisely one extremal exchangeable pair~$\{x,x'\}$ of cluster variables for which the flip of~$x$ to~$x'$ (for any pair of clusters~$\{X,X'\}$ with~$X \ssm \{x\} = X' \ssm \{x'\}$) is in the direction of~$\beta$.
The goal is thus to determine for each positive root which exchangeable pair is extremal.

@@

We are already missing a criterion for exchangeable pairs of walks. See \cite[Sect.~9]{BrustleDouvilleMousavandThomasYildirim}.
It seems that two exchangeable pairs are always kissing along a single distinguishable string.
We need to prove that to see that the non-kissing fan is coherent (because for a pair of exchangeable walks, I can completely reconstruct the $\b{g}$-vector dependence of the flip if I know there distinguished substring).
Note however that
\begin{itemize}
\item exchangeable pairs might kiss along additional non-distinguishable strings (example: just a loop),
\item non-exchangeable walks might kiss along a single distinguishable string (example: see the cyclic triangle in~\cite{PaluPilaudPlamondon}).
\end{itemize}

\bigskip
We have some conjectures on what the extremal exchangeable pairs should be.
One clear (but a bit empty) result is that extremal exchangeable pairs correspond in the Auslander-Reiten quiver to rectangles whose four vertices are non-self-kissing and that cannot be tiled with smaller such rectangles.

>>>>

One important observation is that it seems there is one extremal exchangeable pair for each positive $c$-vector, meaning that for each positive $c$-vector~$\beta$, there is precisely one extremal exchangeable pair~$\{x,x'\}$ of cluster variables for which the flip of~$x$ to~$x'$ (for any pair of clusters~$\{X,X'\}$ with~$X \ssm \{x\} = X' \ssm \{x'\}$) is in the direction of~$\beta$.
The goal is thus to determine for each positive root which exchangeable pair is extremal.
This should be done using the Auslander-Reiten quiver to construct two cluster variables from a $c$-vector (see the next paragraph for the idea).

@@

We are already missing a criterion for exchangeable pairs of walks. See \cite[Sect.~9]{BrustleDouvilleMousavandThomasYildirim}.
It seems that two exchangeable pairs are always kissing along a single distinguishable string.
We need to prove that to see that the non-kissing fan is coherent (because for a pair of exchangeable walks, I can completely reconstruct the $\b{g}$-vector dependence of the flip if I know there distinguished substring).
Note however that
\begin{enumerate}
\item exchangeable pairs might kiss along additional non-distinguishable strings (example: just a loop),
\item non-exchangeable walks might kiss along a single distinguishable string (example: see the cyclic triangle in~\cite{PaluPilaudPlamondon}).
\end{enumerate}

We have some conjectures on what the extremal exchangeable pairs should be.
One clear (but a bit empty) result is that extremal exchangeable pairs correspond in the Auslander-Reiten quiver to rectangles whose four vertices are non-self-kissing and that cannot be tiled with smaller such rectangles.

We checked on some (but probably not enough) small gentle quivers the following properties:
\begin{enumerate}
\item Any $c$-vector (\ie distinguishable string) is the direction of at least one extremal exchangeable pair.
\item Consider a distinguishable string~$\sigma$. Let~$\omega$ (resp.~$\omega'$) be the walk obtained from~$\sigma$ by adding two hooks (resp.~two cohooks) at the endpoints of~$\sigma$. If the walks~$\omega$ and~$\omega'$ are non-self-kissing and exchangeable, then they form the unique extremal exchangeable pair directed by~$\sigma$. These extremal exchangeable pairs correspond to meshes of the Auslander-Reiten quiver.
\item Otherwise, $\sigma$ is the direction to one or more extremal exchangeable pairs obtained by moving further in the Auslander-Reiten quiver (this is really unclear at the moment).
\end{enumerate}
